How to fix IR

### 2017-08-29 political-analysis-draft/draftPA.tex

@@

\begin{table}[ht]
\centering
	\begin{tabular}{l| p{7cm} l}
		& \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
		& &  in a Network Model? \\
		\hline\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & Fails to Replicate \\
		\hline
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		\hline
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
		\hline
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & Fails to Replicate \\ 
		\hline
		Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & Fails to Replicate \\ 
	\hline\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{l|l cc}
~ & ~ & GLM & AME \\
\hline\hline
\multirow{2}{*}{Weeks (2012)} & Area Under ROC Curve (AUC-ROC) & 0.64 & 0.97 \\
~ & Area Under PR Curve (AUC-PR) & 0.004 & 0.15 \\
\hline
\multirow{2}{*}{Reiter \& Stam (2003)} & AUC (ROC) & 0.92 & 0.96 \\
~ & AUC (PR) & 0.08 & 0.15 \\
\hline
\multirow{2}{*}{McDonald (2004)} & AUC (ROC) & 0.92 & 0.99 \\
~ & AUC (PR) & 0.13 & 0.28 \\
\hline
\multirow{2}{*}{Gibler (2017)} & AUC (ROC) & 0.52 & xx \\
~ & AUC (PR) & 0.004 & xx \\
\hline
\multirow{2}{*}{Rose (2004)} & Root Mean Squared Error (RMSE) & 3.23 & 1.99 \\
~ & Root Median Squared Error (RMDSE) & 2.01 & 1.06 \\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
	\begin{tabular}{l| p{7cm} l}
	& \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
	& &  in a Network Model? \\
	\hline\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & \textbf{Fails to Replicate} \\
		\hline
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		\hline
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
		\hline
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & \textbf{Fails to Replicate} \\ 
		\hline
		Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & \textbf{Fails to Replicate} \\ 
	\hline\hline
	\end{tabular}
	\caption{Here we provide a brief summary of the key variable in each of the five replications and a note about whether or not the finding is replicated when using our network based approach. Cases in which the finding is not replicated are highlighted in bold.}
	\label{tab:modelFindingSumm}
\end{table}

@@

\begin{table}[ht]
\centering
	\begin{tabular}{l|l cc}
	~ & ~ & GLM & AME \\
	\hline\hline
		\multirow{2}{*}{Weeks (2012)} & Area Under ROC Curve (AUC-ROC) & 0.64 & \textbf{0.97} \\
		~ & Area Under PR Curve (AUC-PR) & 0.00 & \textbf{0.15} \\
		\hline
		\multirow{2}{*}{Reiter \& Stam (2003)} & AUC (ROC) & 0.92 & \textbf{0.96} \\
		~ & AUC (PR) & 0.08 & \textbf{0.15} \\
		\hline
		\multirow{2}{*}{McDonald (2004)} & AUC (ROC) & 0.92 & \textbf{0.99} \\
		~ & AUC (PR) & 0.13 & \textbf{0.28} \\
		\hline
		\multirow{2}{*}{Gibler (2017)} & AUC (ROC) & 0.52 & \textbf{0.91} \\
		~ & AUC (PR) & 0.00 & \textbf{0.08} \\
		\hline
		\multirow{2}{*}{Rose (2004)} & Root Mean Squared Error (RMSE) & 3.23 & \textbf{1.99} \\
		~ & Root Median Squared Error (RMDSE) & 2.01 & \textbf{1.06} \\
	\hline\hline
	\end{tabular}
	\caption{Here we provide a summary of the out-of-sample performance based on our cross-validation strategy for each of the five replications when using the standard dyadic approach and our network based approach. Four of the five studies involved a binary dependent variable, so for those measures we provide area under the curve (AUC) statistics. The fifth involved a gaussian dependent variable and for that we use the root mean squared error (RMSE) and root median squared error (RMDSE). Cases in which our network based approach outperformed the standard approach are highlighted in bold.}
	\label{tab:modelPerfSumm}
\end{table}
